---
title: "Covid91 vaccine study Final2020"
author: "Jeannet Cendejas"
date: "October 27, 2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode aids to say covid and then remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine.

$H_O$: The preventative vaccine has no effect on whether one contracts the virus or not among the target population.    
$H_A$: The preventative vaccine has an effect on whether one contracts the virus or not among the target population.  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

Every question is of a Cat~Cat.  

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

# Graphical Descriptive Results

```{r}
DataF = filter(FinalData,sex=="gal") 
barchartGC(~infected + treatment,data=DataF)
barchartGC(~infected + treatment,data=DataF, type="percent", main="gals")

```

Among the females who contracted Covid19, twice as many took the placebo. Therefore, it appears that the vaccine has a positive effect.  

```{r}
DataG = filter(FinalData,sex=="guy") 
barchartGC(~infected + treatment,data=DataG)
barchartGC(~infected + treatment,data=DataG, type="percent", main="guys")

```

It appears that the preventative vaccine has a negative effect among the males since they are more likely to contract Covid19 if they get the vaccine.  

```{r}
DataLGBTQ = filter(FinalData,LGBTQ=="gay") 
barchartGC(~infected + treatment,data=DataLGBTQ)
barchartGC(~infected + treatment,data=DataLGBTQ, type="percent", main="gay")

```


```{r}
DataD = filter(FinalData,DrugUser=="yes") 
barchartGC(~infected + treatment,data=DataD)
barchartGC(~infected + treatment,data=DataD, type="percent", main="yes")

``` 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
