---
title: "Covid91 vaccine study Final2020"
author: "Jeannet Cendejas"
date: "October 27, 2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode aids to say covid and then remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine.

$H_O$: The preventative vaccine has no effect on whether one contracts the virus or not among the target population.    
$H_A$: The preventative vaccine has an effect on whether one contracts the virus or not among the target population.  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

Every question is of a Cat~Cat.  

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

# Graphical Descriptive Results

## Analysis for Gals

```{r}
DataF = filter(FinalData,sex=="gal") 
barchartGC(~infected + treatment,data=DataF)
barchartGC(~infected + treatment,data=DataF, type="percent", main="gals")

```

Among the females who contracted Covid19, twice as many took the placebo. Therefore, it appears that the vaccine has a positive effect.    

```{r}
table1 <- xtabs(~infected + treatment, data=DataF)
rowPerc(table1)
colPerc(table1)
```

Among the people who got Covid19 67% took the placebo and 33% took the drug. Among the people who weren't infected 50% took the placebo and 50% took the drug.     

```{r}
fisher.test(table1)
```

This chart displays that the p-value is 2.2e-16. This chart also displays that for people who got the vaccine their odds of getting infected was about 0.5 to 1. So they are 0.5 times less likely to get Covid19 if they got the vaccine which means the vaccine is effective.    

## Analysis for Guys

```{r}
DataG = filter(FinalData,sex=="guy") 
barchartGC(~infected + treatment,data=DataG)
barchartGC(~infected + treatment,data=DataG, type="percent", main="guys")

```

It appears that the preventative vaccine has a negative effect among the males since they are more likely to contract Covid19 if they get the vaccine.    

```{r}
table1 <- xtabs(~infected + treatment, data=DataG)
rowPerc(table1)
colPerc(table1)
```

Among the males who got Covid19 42% took the placebo and 58% took the drug. Among the people who weren't infected 51% took the placebo and 49% took the drug.    

```{r}
fisher.test(table1)
```

This chart displays that the p-value is 0.0005801. This chart also displays that for people who got the vaccine their odds of getting infected was about 1.5 to 1. So they are 1.5 times more likely to get Covid19 if they got the vaccine which means the vaccine is not effective  .


## Analysis for LGBTQ

```{r}
DataLGBTQ = filter(FinalData,LGBTQ=="gay") 
barchartGC(~infected + treatment,data=DataLGBTQ)
barchartGC(~infected + treatment,data=DataLGBTQ, type="percent", main="gay")

```

It appears that the preventative vaccine has a negative effect among the LGBTQ population since they are more likely to contract Covid19 if they get the vaccine.   

```{r}
table1 <- xtabs(~infected + treatment, data=DataLGBTQ)
rowPerc(table1)
colPerc(table1)
```

Among the LGBTQ who got Covid19 29% took the placebo and 71% took the drug. Among the people who weren't infected 51% took the placebo and 49% took the drug.  

```{r}
fisher.test(table1)
```

This chart displays that the p-value is 5.741e-06. This chart also displays that for people who got the vaccine their odds of getting infected was about 2.5 to 1. So they are 2.5 times more likely to get Covid19 if they got the vaccine which means the vaccine is not effective.  

## Analysis for Drug Users

```{r}
DataD = filter(FinalData,DrugUser=="yes") 
barchartGC(~infected + treatment,data=DataD)
barchartGC(~infected + treatment,data=DataD, type="percent", main="drugusers")

``` 

It appears that the preventative vaccine has a positive effect among the drugusers population since they are less likely to contract Covid19 if they get the vaccine.     

```{r}
table1 <- xtabs(~infected + treatment, data=DataD)
rowPerc(table1)
colPerc(table1)
```

Among the drugusers who got Covid19 67% took the placebo and 33% took the drug. Among the people who weren't infected 52% took the placebo and 48% took the drug.

```{r}
fisher.test(table1)
```

This chart displays that the p-value is 0.002273. This chart also displays that for people who got the vaccine their odds of getting infected was about 0.5 to 1. So they are 0.5 times less likely to get Covid19 if they got the vaccine which means the vaccine is effective.  

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
According to charts and numerical summaries, females that got the vaccine are less likely to get Covid19. Among the people who got Covid19 66.89 took the placebo and 33.11 took the drug. Among the people who weren't infected 49.69 took the placebo and 50.31 took the drug. The inferential chart displays that for people who got the vaccine their odds of getting infected was about 0.5 to 1. So they are 0.5 times less likely to get Covid19 if they got the vaccine which means the vaccine is effective. The p-value is 2.2e-16, which means that we reject the null hypothesis as the preventative vaccine had a positive effect in the female population. 

According to charts and numerical summaries, males that got the vaccine are more likely to get Covid19. Among the males who got Covid19 41.84 took the placebo and 58.16 took the drug. Among the males who weren't infected 51.46 took the placebo and 48.54 took the drug. The inferential chart displays that for males who got the vaccine their odds of getting infected was about 1.5 to 1. So they are 1.5 times more likely to get Covid19 if they got the vaccine which means the vaccine is not effective. The p-value is 0.0005801, which means that we reject the null hypothesis as the preventative vaccine had a negative effect in the male population.  

According to charts and numerical summaries, the LGBTQ population that got the vaccine are more likely to get Covid19. Among the LGBTQ who got Covid19 29.31 took the placebo and 70.69 took the drug. Among the people who weren't infected 50.83 took the placebo and 49.17 took the drug. The inferential chart displays that for the gays who got the vaccine their odds of getting infected was about 2.5 to 1. So they are 2.5 times more likely to get Covid19 if they got the vaccine which means the vaccine is not effective. The p-value is 5.741e-06, which means that we reject the null hypothesis as the preventative vaccine had a negative effect in the LGBTQ population.  

According to charts and numerical summaries, the drugusers population that got the vaccine are less likely to get Covid19. In this chart it seemed as if the results for the people who were infected and the people who weren't infected, were almost the same. Among the drugusers who got Covid19 66.67 took the placebo and 33.33 took the drug. Among the people who weren't infected 52.17 took the placebo and 47.83 took the drug. The inferential chart displays that for the drugusers who got the vaccine their odds of getting infected was about 0.5 to 1. So they are 0.5 times more likely to get Covid19 if they got the vaccine which means the vaccine is effective. The p-value is 0.002273, which means that we reject the null hypothesis as the preventative vaccine had a positive effect in the drugusers population.  